The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-05 paper.tex
update

\subsection{X-ray emission}

@@

\subsection{Gamma-ray emission}

@@

\subsubsection{Leptonic process}
In the leptonic scenario, the gamma-rays originate from IC scattering of the ISRF by CRe.\
The CRe spectrum follows a power law distribution\
with a spectral index $p=2.4$ and ranges from\
$m_{\text{e}}c^2$ ($0.5$ MeV) to $1.1\times10^{6}m_{\text{e}}c^2$ ($550$ GeV).\

>>>>

\subsection{X-ray}

@@

\subsection{Microwave haze}

  \begin{subequations}
     \begin{align}
        &I_{\nu} = \frac{4\pi\mathbb{C}e^{3}B^{0.5(p+1)}}{m_{\text{e}}c^{2}}\
        \left(\frac{3e}{4\pi m_{\text{e}}c}\right)^{0.5(p-1)}\
        a(p)\nu^{-0.5(p-1)}.\\
        &a(p)=\nonumber\\
             &\frac{2^{0.5(p-1)}\sqrt{3}\Gamma\left[\left(3p-1\right)/12\right]\
                                        \Gamma\left[\left(3p+9\right)/12\right]\
                                        \Gamma\left[\left(p+5\right)/4\right]}
        {8\sqrt{\pi}(p+1)\Gamma\left[\left(p+7\right)/4\right]}
     \end{align}
  \end{subequations}

\subsection{Gamma-ray}

@@

In the leptonic scenario, the gamma-rays originate from IC scattering of the ISRF by CRe.\
The CRe spectrum follows a power law distribution\
with a spectral index $p=2.4$ and ranges from\
$m_{\text{e}}c^2$ ($0.5$ MeV) to $1.1\times10^{6}m_{\text{e}}c^2$ ($550$ GeV).\
